JEThread: A Thread Pool Implementation in C

### 2018-05-04 thread-pool-implementation/paper.tex

\usepackage{graphicx}   % Written by David Carlisle and Sebastian Rahtz
                        % Required if you want graphics, photos, etc.
                        % graphicx.sty is already installed on most LaTeX
                        % systems. The latest version and documentation can
                        % be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/graphics/
                        % Another good source of documentation is "Using
                        % Imported Graphics in LaTeX2e" by Keith Reckdahl
                        % which can be found as esplatex.ps and epslatex.pdf
                        % at: http://www.ctan.org/tex-archive/info/
\usepackage{xcolor}
%\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
                        % and David Carlisle
                        % This package allows you to substitute LaTeX
                        % commands for text in imported EPS graphic files.
                        % In this way, LaTeX symbols can be placed into
                        % graphics that have been generated by other
                        % applications. You must use latex->dvips->ps2pdf
                        % workflow (not direct pdf output from pdflatex) if
                        % you wish to use this capability because it works
                        % via some PostScript tricks. Alternatively, the
                        % graphics could be processed as separate files via
                        % psfrag and dvips, then converted to PDF for
                        % inclusion in the main file which uses pdflatex.
                        % Docs are in "The PSfrag System" by Michael C. Grant
                        % and David Carlisle. There is also some information
                        % about using psfrag in "Using Imported Graphics in
                        % LaTeX2e" by Keith Reckdahl which documents the
                        % graphicx package (see above). The psfrag package
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/psfrag/

@@

\section{Evaluation}
Below is the hardware we used to conduct experiements on the performance of the thread pool.
	\begin{table}[!hbt]
		% Center the table
	\begin{center}
		\caption{Hardware Sepcification}
		\label{tab:simParameters}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			Processor & Intel® Core™ i7-6700 CPU \\
								&@3.40GHz $\times$ 8\\
			\hline
			RAM & $15.6$ GiB \\
			\hline
			OS & Ubuntu 16.04.4 LTS 64-bit\\
			\hline
		\end{tabular}
		\end{center}
	\end{table}

@@

@@

\section{Conclusion}
	Write something here lol

>>>>

\usepackage{graphicx}   % Written by David Carlisle and Sebastian Rahtz
                        % Required if you want graphics, photos, etc.
                        % graphicx.sty is already installed on most LaTeX
                        % systems. The latest version and documentation can
                        % be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/required/graphics/
                        % Another good source of documentation is "Using
                        % Imported Graphics in LaTeX2e" by Keith Reckdahl
                        % which can be found as esplatex.ps and epslatex.pdf
                        % at: http://www.ctan.org/tex-archive/info/
\usepackage{color}
%\usepackage{psfrag}    % Written by Craig Barratt, Michael C. Grant,
                        % and David Carlisle
                        % This package allows you to substitute LaTeX
                        % commands for text in imported EPS graphic files.
                        % In this way, LaTeX symbols can be placed into
                        % graphics that have been generated by other
                        % applications. You must use latex->dvips->ps2pdf
                        % workflow (not direct pdf output from pdflatex) if
                        % you wish to use this capability because it works
                        % via some PostScript tricks. Alternatively, the
                        % graphics could be processed as separate files via
                        % psfrag and dvips, then converted to PDF for
                        % inclusion in the main file which uses pdflatex.
                        % Docs are in "The PSfrag System" by Michael C. Grant
                        % and David Carlisle. There is also some information
                        % about using psfrag in "Using Imported Graphics in
                        % LaTeX2e" by Keith Reckdahl which documents the
                        % graphicx package (see above). The psfrag package
                        % and documentation can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/psfrag/

@@

\section{Evaluation}
Below is the hardware we used to conduct experiements on the performance of the thread pool.
	\begin{table}[!hbt]
		% Center the table
	\begin{center}
		\caption{Hardware Sepcification}
		\label{tab:simParameters}
		% Table itself: here we have two columns which are centered and have lines to the left, right and in the middle: |c|c|
		\begin{tabular}{|c|c|}
			% To create a horizontal line, type \hline
			\hline
			% To end a column type &
			% For a linebreak type \\
			Processor & Intel® Core™ i7-6700 CPU \\
								&@3.40GHz $\times$ 8\\
			\hline
			RAM & $15.6$ GiB \\
			\hline
			OS & Ubuntu 16.04.4 LTS 64-bit\\
			\hline
			Compiler & GCC 5.40\\
			\hline
		\end{tabular}
		\end{center}
	\end{table}

@@

\newpage

@@

\section{Conclusion}
	Theoratically, thread pool can be very efficient especially dealing with a large number of relatively short tasks concurrently. In order to acheive maximum performance boost, the use of context switch should be minimized. The thread pool does a greate job of reducing the overhead in context switch. In addition, work stealing further facilitates the work throughput by letting idle threads execute other threads' tasks. However, thread pool is not a silver bullet that solves every problem of thread. The overhead of thread context switch is transfered to each thread's task queue as executing tasks requires dequeing the task each time, which also applies to job stealing. We've also conducted experiement with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transfered to the queue since accessing tasks is performed with lock's protection. In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unware of the actual workload in its distribution target. The work stealing is also very tricky to implement as the stealer is not aware of the workload distribution during runtime. If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck that causes main threads waiting unnecessarily. Additional improvements such that runtime dynamic workload check and compiler support for user-guided optimization will further increase the usibility of thread pool.\\

	In summary, the thread pool is great for running a large amount of tasks effciently with relatively small number of threads. In parallel applications with many short tasks to perform thread will be a strong candidate solution.
